Analysis

### 2018-06-29 reports/analysis_pilot.Rmd
save plot
for OPAM

```{r}
df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  xlab("Quintile") + 
  theme(text = element_text(size=14))

>>>>

```{r}
p <- df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  xlab("Quintile") + 
  theme(text = element_text(size=14))
p
ggsave(here::here("plots", "opam_figure.eps"), p, width = 6, height = 6)
